---
title: "PTR-75-GMAP matrix Ptr Pan Genomes"
author: "Paula Moolhuijzen"
date: "Date: `r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

libraries loaded

```{r, echo=FALSE, message=FALSE, include=FALSE}
getwd()
setwd(getwd())
print(getwd())
```


```{r, echo=FALSE, message=FALSE, include=FALSE}

library(ggplot2)
library(gplots)
library(pheatmap)
library("dplyr")
library("ggpubr")
library("Hmisc")
library(corrplot)
library(reshape2)
#library(ggridges)
library(grid)
library(gridExtra)
library(lattice)
library(RColorBrewer)
```

Read in Ptr gene matrix sequence percent identity

```{r, echo=TRUE,message=TRUE}

mat <- as.matrix(read.table("matrix-pid.txt", row.names=1, header=TRUE))

dim(mat)
```

filter out genes with the same sequence percent identity across all isolates

```{r, echo=TRUE,message=TRUE}

df <- mat[apply(mat, 1, function(x) length(unique(x[!is.na(x)])) != 1),]

dim(df)
```


```{r}
meta <- as.data.frame(read.table("meta.txt", sep="\t", header = TRUE, row.names=1 ))

```


Correlation plot for all mRNA sequence percent identity

```{r, echo=FALSE, fig.width=8, fig.height=8}

ann_colors = list(
    Country = c(Australia="#0066CC", Canada="firebrick", USA="#009900", Algeria="#EED8BD", Tunisia="#D1B28A", UK="#D9A7E8", Germany="#C270DB", Denmark="#A436C6", Brazil="#6600CC"),
    Technology = c(Illumina = "#E0E0E0", PacBio = "#A0A0A0", ONT="#606060", Sanger="#A0A0A0"),
    Race = c(race1 = "#009900", race2 = "orange", race3 = "#6600CC", race4 = "#0066CC", race5 = "#FFD700", race7 = "firebrick", race8= "black", na="white", unknown="#D2B48C")
)

labs.row <- rownames(cor(mat))
labs.row <- gsub("\\.","-",labs.row )

labs.col <- colnames(cor(mat))
labs.col <- gsub("\\.","-",labs.col )

pheatmap(cor(mat), annotation_row = meta, show_rownames=T, show_colnames=T, fontsize=12, annotation_colors = ann_colors, labels_row=labs.row, labels_col=labs.col)

```

Read in Ptr  matrix of gene counts

```{r, echo=TRUE,message=TRUE}

mat1 <- as.matrix(read.table("matrix-cnt.txt", row.names=1, header=TRUE))

dim(mat1)
```

filter genes out with the same number of counts across isolates

```{r, echo=TRUE,message=TRUE}


df1 <- mat1[apply(mat1, 1, function(x) length(unique(x[!is.na(x)])) != 1),]


```


Plot the correlation for all gene counts

```{r, echo=FALSE, fig.width=10, fig.height=12}


labs.row1 <- rownames(cor(mat1))
labs.row1 <- gsub("\\.","-",labs.row )

labs.col1 <- colnames(cor(mat1))
labs.col1 <- gsub("\\.","-",labs.col )


pheatmap(cor(mat1), annotation_row = meta, fontsize=12, annotation_colors = ann_colors, labels_row=labs.row1, labels_col=labs.col1)

```


Plot correlation for filtered gene count

```{r, echo=FALSE, fig.width=10, fig.height=12}

pid <- pheatmap(cor(mat), show_rownames=T, show_colnames=T, annotation_row = meta, fontsize=12, annotation_colors = ann_colors, main="A", labels_row=labs.row, labels_col=labs.col)
  
cnt <- pheatmap(cor(mat1), show_rownames=T, show_colnames=T, annotation_row = meta, fontsize=12,annotation_colors = ann_colors, main="B", labels_row=labs.row1, labels_col=labs.col1)

```

```{r}
plot_list=list()
plot_list[["pid"]]=pid[[4]]
plot_list[["cnt"]]=cnt[[4]]

pdf(file="correlation-pid-cnt.pdf", width=18, height = 12)
grid.arrange(grobs=plot_list, ncol=2)
dev.off()
```


Filter genes for ToxC producing isolates counts absent/present Pacbio

```{r, fig.width=10, fig.height=12}
dfp <- df1[,c("DW5","Ls13.192","Ptr86.124","Ptr90.2","Biotrigo9.1","V1","M4","ARCrossB10","Pt.1C.BFP")]

list <- list("DW5","Ls13.192","Ptr86.124","Ptr90.2","Biotrigo9.1","V1","M4","ARCrossB10","Pt.1C.BFP")
f1 <-dfp[grep("V1|DW5|Ls|Ptr86|Ptr90|Bio|M4|ARC|PTR", rownames(dfp)),]

f1 = f1[f1[,"DW5"] == 0,]
f1 = f1[f1[,"Ls13.192"] == 0,]
f1 = f1[f1[,"Ptr86.124"] == 0,]
f1 = f1[f1[,"Ptr90.2"] == 0,]
f1 = f1[f1[,"Biotrigo9.1"] == 0,]
f1 = f1[f1[,"V1"] != 0,]
f1 = f1[f1[,"M4"] != 0,]
f1 = f1[f1[,"ARCrossB10"] != 0,]
#f1 = f1[f1[,"Pt.1C.BFP"] != 0,]


pdf(file="matrix-ToxC.pdf", width = 10, height=12)

pheatmap(f1, fontsize_col = 8, fontsize_row = 6, show_rownames=T)

dev.off()
```

```{r}
sessionInfo()
```

